---
title: "Challenge 2"
author: Ryan Wesslen
date: July 27, 2016
output: html_document
---

#### Supervised machine learning

Use the same dataset from Challenge 1. In this exercise, we're going to use supervised machine learning to determine the different words used by point Tweets versus polygon Tweet. Our goal is to better understand how Tweet content differs based on geo-location type.

1. Reload the dataset and `functions.R`. Change the geo.code column to a factor (`factor` function). We will build a machine learning classifier to determine the words that most characterize each geo-location type.

```{r}

```

2. Create a training and test set, with 80% and 20%, respectively.

```{r}

```

3. Construct the DFM. You may want to experiment with different preprocessing techniques until you achieve better performance.

```{r}

```

4. Now run the classifier. Then, compute the accuracy.

```{r}

```

5. Identify the features that better predict that tweets the geo-location. What do you learn?
```{r}

```

BONUS. 

```{r}

```


