---
title: "Challenge 1"
author: Ryan Wesslen (modified)
date: July 27, 2016
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=TRUE, warning=FALSE, message=FALSE)
```

#### Descriptive analyses of text

Our goal is to learn how to find specific Tweets. The goal: find Carolina Panther Tweets.

The dataset is a 20% sample of all Charlotte geo-located Tweets in a three month period (Dec 1 2015 to Feb 29 2016).  

1. Read in the data. Run the `functions.R` file with pre-created functions. 

 * First, plot the dataset using the `timePlot` function. Add the parameter "smooth = TRUE" to add a smoothing parameter. 

 * What is causing the spikes?

```{r}

```

2. Save the most common hashtags (function `getCommonHashtags`); make sure to use the Tweet text (body) as the input. What are the top 10 hashtags?

 * Repeat the same exercise with the handle function (`getCommonHandles`). 

 * Modify to the top 25 handles and hashtags.

```{r}

```

3. Choose hashtags and handles that you think will best identify Carolina Panther Tweets. 

  * put the hashtags and handles into a character vector: names <- c("keyword1","keyword2")

  * use `paste(names, collapse = "|")` to create a string of the keywords (with | as an OR). In a `grepl` function on the lower case of the Tweet's text, create a new column of what rows meet your criteria.

  * Use your new column vector as a row filter on the original datset. Run your new panthers dataset through `timePlot`.
  
Determine how many Panther Tweets you can identify for this period. Are these all Panther Tweets?

```{r}

```

4. Create a dfm with the body variable on the entire dataset (raw.tweets) using the `quanteda` package. Add in the covariate panthers dummy variable (hint: use the `docvars` function after you create your corpus). 

 * Run basic pre-processing, run the top 10 word counts (`topfeatures` function) and create a word cloud.

 * Rerun the word cloud but tfidf weighting. What's the difference?

```{r}

```

5. Rerun the dfm but this time add in the geo.type as a group. Run a comparison word cloud (`comparison = TRUE`). This may take a few minutes.

 * What are the differences in content between points and polygon Tweets? Replot the time series, this time creating one plot for each geo.type ()

```{r}

```

BONUS. Additional pre-processing steps can sometimes improve results. Run additional pre-processing steps including: stemming, Twitter mode, bigrams or trigrams. Use ?dfm help to get a list of the parameters. 

* Rerun your word clouds. What difference did these pre-processing steps make?

* Did you find new words to describe Carolina Panther Tweets?

```{r}

```
